
```{r include = FALSE}
require(rmarkdown); require(knitr); require(sevenbridges); require(readr);

options(max.print = "99"); opts_knit$set(width = 99); opts_chunk$set(cache=FALSE, tidy=FALSE)

source("~/sbg_auth.R")

```

<hr>

Wrapping of vcf2maf for use in any cwl compatible platform.

## base command

```{sh base command, eval=FALSE}

vcf2maf... [fill this out]

```

## docker 

docker file

https://github.com/teamcgc/vcf2maf/Dockerfile

The docker conatiner is

``` teamcgc/vcf2maf:latest ```

Docker image should be built off master repo probably since no changes have been made.

## App ports {.tabset .tabset-fade .tabset-tabs}

### Inputs

```{r inputs, eval=run.mode=="push"}
inputs = list(
  
input(id = "vcf", label = "vcf", description = "vcf", type = "File")

)

```

### Outputs

```{r output, eval = run.mode=="push"}

outputs = list(

output(id = "maf", label = "maf", 
description = "maf", type = "File",
metadata = list(org = "cgp"),
glob = "\"*.maf\""),


output(id = "std_out", label = "std_out", 
description = "standard output", type = "File...",
metadata = list(org = "cgp"),
glob = "\"std.out\"")
  
)



```

## Define Tool Object and Push to Platform {.tabset .tabset-fade .tabset-tabs}
  
### Tool object

```{r 5 create tool object, eval=run.mode=="push"}

tool <- Tool(
id = "vcf2maf",
label = "vcf2maf",
hints = requirements(docker(pull = "teamcgc/vcf2maf:latet"), cpu(1), mem(1000)),
baseCommand = "perl vcf2maf.pl --input-vcf data/test.vcf --output-maf test.vep.maf
",
stdout = "std.out",
inputs = inputs,
outputs = outputs
)


```

### Make cwl file

```{r make cwl, eval=destination=="platform"}

write(tool$toJSON(pretty = TRUE), "vcf2maf_cwl.json")

```

### Push app to sbg platform

```{r push app to sbg, eval=destination=="platform"}

project$app_add("vcf2maf", tool)

```

